A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-12-19 manuscript/manuscript.tex
added t2 study and freesurfer

A healthy volunteer was scanned using a 3T Siemens Skyra with a 32-channel head
and neck coil to demonstrate the application of analyses implemented in
Arcana. The protocol was a T1-weighted MPRAGE (1mm contiguous,
matrix size 256x240x192, FOV 256x240x192, TE = 2.13ms, TR, = 2300ms, TI
= 900ms, bandwidth = 230Hz/pixel), GRE (1.8 mm contiguous, matrix size
256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
bandwidth = 120Hz/pixel), and diffusion MRI (1.2 mm contiguous, matrix size
110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
directions with b = 1500 mm2/s and 3 b=0, bandwidth = 781Hz/pixel).

>>>>

A healthy volunteer was scanned using a 3T Siemens Skyra with a 32-channel head
and neck coil to demonstrate the application of analyses implemented in
Arcana. The protocol was a T1-weighted MPRAGE (1mm contiguous,
matrix size 256x240x192, FOV 256x240x192, TE = 2.13ms, TR, = 2300ms, TI
= 900ms, bandwidth = 230Hz/pixel), GRE (1.8 mm contiguous, matrix size
256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
bandwidth = 120Hz/pixel), and diffusion MRI (2 mm contiguous, matrix size
110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
directions with b = 1500 mm2/s and 3 b=0, bandwidth = 781Hz/pixel).
